Capture and Replay Tools in the Field

### 2017-04-28 paper.tex
Added citations from Deepa

\par
JARDIS \cite{paperA}, a time-traveling debugger for JavaScript. It is part of Microsoft’s ChakraCore JavaScript engine and a fork of the Node.js runtime environment . The overall system design is a record-replay-snapshot architecture. The snapshot algorithm is based on \cite{paperB} with the record-replay work done in the JsRT hosting API layer  that Node.js uses to interface with the JavaScript runtime. 
It provides a rich set of functionality for recording and navigating the execution history of a program including: \\

>>>>

\par
JARDIS \cite{time-travel-debugging-javascriptnode-js}, a time-traveling debugger for JavaScript. It is part of Microsoft’s ChakraCore JavaScript engine and a fork of the Node.js runtime environment . The overall system design is a record-replay-snapshot architecture. The snapshot algorithm is based on \cite{Barr:2014:TAT:2714064.2660209} with the record-replay work done in the JsRT hosting API layer  that Node.js uses to interface with the JavaScript runtime. 
It provides a rich set of functionality for recording and navigating the execution history of a program including: \\
